ShrinkNets: Learning Network Size while Training

### 2018-02-09 paper/ICML/introduction.tex
Update introduction.tex

Of course, the problem of finding compressed or small networks is not new.
Existing techniques to make a pre-trained neural network smaller can be
categorized in two approaches: (1) quantization \cite{Jouppi:2017:IPA:3079856.3080246} and code
compilation, techniques that can be applied blindly to
any network, and (2) techniques which analyze the structure of the network and
systematically prune connections or neurons~\cite{han2015deepcompression,Cun}. 
While the first category is always useful, but only
has limited impact on the network size, the second category can reduce the model
size much more but has several drawbacks:   First, those techniques often
negatively impact model quality.  Second, they can (surprisingly) negatively
impact inference time as they transform dense matrix operations into sparse
ones, which can be substantially slower to execute on GPUs which do not support
efficiently sparse linear algebra\cite{han2015deepcompression}. 
Third, these techniques generally start by optimizing a
particular architecture for prediction performance, and then, as a post-
processing step, applying compression  to generate a smaller model that meets
the resource constraints of the deployment setting.  Because the network
architecture is essentially fixed during this post-processing,   model
architectures that work better in small settings may be missed -- this is
especially true in large networks like many-layered CNNs,  where it is
infeasible to try explore even a small fraction of possible network
configurations.

>>>>

Of course, the problem of finding faster and smaller networks is not new.
Existing techniques to make a pre-trained neural network smaller can be
categorized in two approaches: (1) quantization \cite{Jouppi:2017:IPA:3079856.3080246} and code
compilation, techniques that can be applied blindly to
any network, and (2) techniques which analyze the structure of the network and
systematically prune connections or neurons~\cite{han2015deepcompression,Cun}. 
While the first category is always useful, but only
has limited impact on the network size, the second category can reduce the model
size much more but has several drawbacks:   First, those techniques often
negatively impact model quality.  Second, they can also (surprisingly) negatively
impact inference time as they transform dense matrix operations into sparse
ones, which can be substantially slower to execute on GPUs which do not support
efficiently sparse linear algebra\cite{han2015deepcompression}. 
Third, these techniques generally start by optimizing a
particular architecture for prediction performance, and then, as a post-
processing step, applying compression  to generate a smaller model that meets
the resource constraints of the deployment setting.  Because the network
architecture is essentially fixed during this post-processing,   model
architectures that work better in small settings may be missed -- this is
especially true in large networks like many-layered CNNs,  where it is
infeasible to try explore even a small fraction of possible network
configurations.
